\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-13 09-30-2014]

### 2014-10-02 paper.tex

There are a number of algorithms for developing policies to balance exploration and exploitation.
One algorithm is $\epsilon-$greedy, which is the idea of choosing the arm with the highest empirical expected reward with $1-\epsilon$ probability and choosing a random arm with probability $\epsilon$ \cite{barto1998reinforcement}.
A class of algorithms that have theoretical guarantees are Upper Confidence Bound (UCB).
UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times has been sampled for each arm.
The algorithm chooses the arm at each step which has the highest upper bound on expected reward, since that is the most potentially promising arm.
When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the number of times a sub-optimal arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance \cite{kuleshov}.

\subsection{Budgeted Multi-Arm Bandit Problem and Grasping}
%In the problem of choosing the best grasp, one must intelligently allocate samples based on the observations received so far.
%As you can in Fig. \ref{fig:sampling_convergence}, a typical grasp can take hundreds of iterations for convergence of the expected value to be reach.
%Thus if one had 1000 grasps to choose from, it would take on the order of millions grasp metric evaluations to choose the best grasp in the naive way.
%If we can develop a policy to intelligently explore the proposed grasps and select the best one, we can reduce the computationally complexity of grasping with uncertainty.

In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
We can formulate this problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling the shape representation and evaluating the arm's grasp plan on the sampled shape representation.
The reward for pulling an arm is the grasp quality of the resulting grasp on the sampled shape.
We have a policy for exploration of different grasp plans (i.e. choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far, which would correspond to actually performing the grasp.

We measured performance of our polices in terms of simple regret, which is the difference of the true expected value of the actual best grasp plan and the true expected value of the selected grasp plan at the given stopping time \cite{bubeck2009pure}.
The number of samples needed before the simple regret reaches zero, determines how effective an exploration  policy is for grasp evaluation.

\todo{Add Multi arm bandit preliminary make it long}

@@

\subsection{Line of Action}
Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}. A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.  Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}. While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. Future work will look at how to efficiently sample when the approach trajectory has noise.

Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model and set of possible grasp plans $G$. We are interested in determining

\section{Multi-Arm Bandit for Grasp Selection}
While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample.

\subsection{Our Implementation}
In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration. Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form. Thus, we are restricted in the type of bandit policies available to us, since most sophisticated polices require distributional information. \todo{double check with Dylan}

Let $\hat{\mu_i}$ be the sample mean of the grasp quality for grasp plan $i$.  Thus the confidence interval for grasp plan $i$ is $[\hat{\mu_i} - C_i, \hat{\mu_i} + C_i]$ \cite{caflisch1998monte}.  
After a sample from a grasp plan, we check to see if the confidence interval of the sampled grasp intersects with the confidence interval of the current best grasp plan, and if it does not, we prune that grasp plan from the current active set of  grasp plans. Since we prune grasps that our below a confidence interval we have statistical guarantees unlike earlier approaches to this problem\cite{kehoe2012toward}. In future work, we will look at using other exploration strategies.

>>>>

There are a number of algorithms for developing policies to balance exploration and exploitation.
One algorithm is $\epsilon-$greedy, which is the idea of choosing the arm with the highest empirical expected reward with $1-\epsilon$ probability and choosing a random arm with probability $\epsilon$ \cite{barto1998reinforcement}.
A class of algorithms that have theoretical guarantees are Upper Confidence Bound (UCB).
UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times has been sampled for each arm.
The algorithm chooses the arm at each step which has the highest upper bound on expected reward, since that is the most potentially promising arm.
When the rewards come from exponential family distribution, UCB minimizes cumulative regret, which is the number of times a sub-optimal arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.

We can formulate our problem as a "budgeted multi-arm bandit problem" \cite{madani2004budgeted}.
The budgeted multi-arm bandit problem has a finite stopping time.
The objective of the budgeted multi-arm bandit problem is to minimize the "simple regret", which is the difference between the true expected value of the actual best arm and the true expected value of the arm pulled at the stopping time.
Thus the budgeted multi-arm bandit problem reduces to exploration until the very last time step, at which time one exploitation step is taken.

\subsection{Line of action}
Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
\todo{move the next two lines}
While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
Future work will look at how to efficiently sample when the approach trajectory has noise.

Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model (we will describe the GPIS model later) and set of possible grasp plans $G$.
We are interested in determining

\subsection{Multi-Arm Bandits for Grasp Selection}
While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample. 
In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling the shape representation and evaluating the arm's grasp plan on the sampled shape representation.
The reward for pulling an arm is the grasp quality of the resulting grasp on the sampled shape.
We have a policy for exploration of different grasp plans (i.e. choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far, which would correspond to actually performing the grasp.  
The number of samples needed before the simple regret reaches zero, determines how effective an exploration policy is for grasp evaluation.

In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $E(Q(\Gamma))$ determined via Monte-Carlo Integration.
Due to the non-linear nature of our grasp metric, we currently do not have a way to represent the distribution on grasp quality of $p(Q(\Gamma))$ in closed form.
Thus, we are restricted in the type of bandit policies available to us, since most sophisticated polices require distributional information. \todo{double check with Dylan}

Let $\hat{\mu_i}$ be the sample mean of the grasp quality for grasp plan $i$.
Then the confidence interval for grasp plan $i$ is $[\hat{\mu_i} - C_i, \hat{\mu_i} + C_i]$ \cite{caflisch1998monte}.  
After a sample from a grasp plan, we check to see if the confidence interval of the sampled grasp intersects with the confidence interval of the current best grasp plan, and if it does not, we prune that grasp plan from the current active set of  grasp plans. Since we prune grasps that our below a confidence interval we have statistical guarantees unlike earlier approaches to this problem\cite{kehoe2012toward}. In future work, we will look at using other exploration strategies.

@@
